The impact of cosmic variance on simulating weak lensing surveys

### 2014-10-22 Writeup/paper_v3.tex
tweak / modify discussion of fits to volume-limited redshift distributions

The functional forms for the (flux-limited) redshift distribution that we used in Sec.~\ref{sub:overdensities} are not physically motivated. We try to fit them again to the  
redshift distribution of a volume-limited sample ($M_I < -22$). 
Due to the absence of an exponential tail in the histogram, the parameters that set the scale for the redshift, $z_1$ and $z_2$ run to 
incredible large values during the fit, making $p_1(z)$ and $p_2(z)$ defined in Eq.~\eqref{E:pz1} and Eq.~\eqref{E:pz2} essentially the same power law.
The best fit exponent is remarkably close to $2$ suggesting that the number of galaxies within a given comoving volume grows proportional to the volume itself. 
Fig.~\ref{fig:redshift_vollimited} shows that when we do
this, the values of $\delta_{g,\text{1D}}$ for the $z=0.40-0.55$ bin
increase and are within the $[-0.1, 0.1]$ range that we have defined
as neutral. This is the reason that in Sec.~\ref{sub:overdensities} we classified them as neutral as opposed to underdense.
We will see in Sec.~\ref{S:results} that they are more similar to overdense regions as opposed to underdense regions.
The other redshift slices seem to exhibit a consistent behavior in
Fig.~\ref{fig:redshift_vollimited} as in Fig.~\ref{fig:redshift_fluxlimited}.

\begin{figure}
 \centering
  \includegraphics[width=\columnwidth]{redshift_vollimited}
  \caption{
Upper panel: Redshift distribution of volume-limited ($M_I <  -22$)
sample with photometric redshift bins that are 0.05 wide. Two
analytical functions with best fit parameters are plotted over it. 
The best fit parameters for $p_1(z)$ are $a=2.78\pm0.28$.
           Lower panel: Plot of $(1+\delta_{g,\text{1D}}) =
           N/N_{\text{mod}}$ with each functional form as the model
           for each redshift bin. \rachel{I am quite concerned that
             something has gone wrong with this fit (in the sense that
           there may be a bug).  Why is the redshift distribution
           shown in blue forced to zero at $z=0.3$?  It should go to
           zero at $z=0$, not $0.3$.  It is clearly not normalized to the same total number as the redshift histogram, either.  In terms of formatting, please
           implement the same changes that I suggested for the
           flux-limited sample redshift distribution plot.}\arun{This will change once I discuss with you.}} 
  \label{fig:redshift_vollimited}
\end{figure}

>>>>

The functional forms for the (flux-limited) redshift distribution that
we used in Sec.~\ref{sub:overdensities} are not well-motivated for a
volume-limited sample. If we fit them to the 
redshift distribution of the volume-limited sample ($M_I < -22$
\rachel{without or with evolution correction?}), then 
due to the absence of an exponential tail in the histogram, the
parameters that set the scale for the redshift ($z_1$ and $z_2$)
become very large.  As a result, both  $p_1(z)$ and $p_2(z)$ defined
in Eqs.~\eqref{E:pz1} and~\eqref{E:pz2} essentially become the same power law.
The best-fitting exponent is remarkably close to $2$ ($a=2.78\pm
0.28$, giving an exponent $1.78\pm 0.28$), suggesting that the
comoving number density of galaxies is constant with redshift as we
would expect for a volume-limited sample in a redshift range for which
evolution is negligible. 
Fig.~\ref{fig:redshift_vollimited} shows that when we do
this, the values of $\delta_{g,\text{1D}}$ for the $z=0.40-0.55$ bin
increase and are within the $[-0.1, 0.1]$ range that we have defined
as neutral. This is the reason that in Sec.~\ref{sub:overdensities} we classified them as neutral as opposed to underdense.
We will see in Sec.~\ref{S:results} that they are more similar to overdense regions as opposed to underdense regions.
The other redshift slices seem to exhibit a consistent behavior in
Fig.~\ref{fig:redshift_vollimited} as in Fig.~\ref{fig:redshift_fluxlimited}.

\begin{figure}
 \centering
  \includegraphics[width=\columnwidth]{redshift_vollimited}
  \caption{
Upper panel: Redshift distribution of volume-limited ($M_I <  -22$)
sample with photometric redshift bins that are 0.05 wide. Two
analytical functions with best fit parameters are plotted over it, as
discussed in the text. 
           Lower panel: Plot of $(1+\delta_{g,\text{1D}}) =
           N/N_{\text{mod}}$ with each functional form as the model
           for each redshift bin. } 
  \label{fig:redshift_vollimited}
\end{figure}
